---
title: "Models of Dissolved Organic Carbon in Water"
author: "Ivan Lysiuchenko"
date: "August 6, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Original Data and Our Application

- The original dataset is related to the work

Van Leeuwen, J., J. Awad, D.J. Chittleborough, E. Bestland, J.W. Cox, M. Drikas, C. Chow and R.J. Smernik, 2017.  ARC LP 110200208 (2012-2016): Impact of natural organic carbon and nutrients on water quality: Identification of catchment sources and attenuation processes.  UniSA Research Data Access Portal, University of South Australia.

- Link to download the data:
<https://data.unisa.edu.au/Dataset.aspx?DatasetID=273951>

- Links to our application:
<https://ivanlis.shinyapps.io/shiny_water/>
<https://github.com/ivanlis/course09week4project.git> (shiny_water directory)

## Data Preprocessing

This is how the data are read and preprocessed by the server:

```{r echo=FALSE, message=FALSE}
library(openxlsx)
library(dplyr)
```


```{r echo=TRUE, message=FALSE}
waterOrg <- read.xlsx("../shiny_water/treatability_organic.xlsx", 
                      sheet = 2, rows = 11:320, cols = 1:10, 
                          na.strings = c("NA", "--", "---", ""))
names(waterOrg) <- c("sample", "site", "surface_subsurface", 
                     "collection_method", "raw_treated", 
                     "alum_dose", "ph", "uv254", "color", "doc")
waterOrg <- waterOrg %>% 
    filter(!is.na(ph) & !is.na(uv254) & !is.na(color) & 
        !is.na(doc) & (!is.na(alum_dose) | raw_treated == "Raw"))
waterOrg[waterOrg$raw_treated == "Raw", "alum_dose"] = 0
```

## Computing the Model

A (Multiple) Linear Regression model is built like this:

```{r echo=TRUE, message=FALSE}
model <- lm(data = waterOrg, formula = doc ~ color + uv254)
```

The user is able to work with a subset of the dataset (the 'Water Source' input),
as well as to modify the set of predictors ('Predictors to use'):

- formula = doc ~ color
- formula = doc ~ uv254
- formula = doc ~ color + uv254
- formula = doc ~ color * uv254
- formula = doc ~ color + uv254 + ph


## Model Summary and Residuals

The model summary is shown:

```{r echo=TRUE, message=FALSE}
summary(model)$coef
```

Also the diagnostic residual plots are provided:

```{r echo=TRUE, message=FALSE, eval=FALSE}
par(mfrow = c(2,2))
plot(model)
```
